Distrivia: A Distributed Trivia Game

### 2011-04-23 papers/phase-two/paper.tex

\subsection {Traffic}
We have two load sharers set up. Both sharers are currently configured to
divide the requests among the three active servers and, if need be, the two hot spares. The duplicate sharers allow
for a load distributer to go down and we would still be able to serve requests
to the servers. These load sharers are selected by the clients using round
robin DNS where distrivia.lame.ws will select either load distributer that is
up at random. If a load distributer should go down or become unreachable the
DNS service will no longer serve that hosts DNS record until it is again
reachable. This provides us with stability for accessing the servers. The
load sharers are setup to attempt to connect to a server twice in a one second
period before deeming it dead and removing it from its list of servers to direct clients towards.
Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
for our load sharing needs.

>>>>

\subsection {Traffic}
We have two load sharers set up. Both sharers are currently configured to
divide the requests among the three active servers and, if need be, the two hot spares. The duplicate sharers allow
for a load distributer to go down and we would still be able to serve requests
to the servers. These load sharers are selected by the clients using round
robin DNS where distrivia.lame.ws will select either load distributer that is
up at random. If a load distributer should go down or become unreachable the
DNS service will no longer serve that hosts DNS record until it is again
reachable. This provides us with stability for accessing the servers. The
load sharers are set up to attempt to connect to a server twice in a one second
period before deeming it dead and removing it from its list of servers to direct clients towards.
Currently we are using the NGINX \cite{nginx} in a reverse proxy configuration
for our load sharing needs.
